---
title: "Exploration_file"
output: pdf_document
date: 2022-10-12
authors: null
---

```{r installation, message=FALSE, warning=FALSE, include=FALSE}
# load packages
#install.packages("tidyverse", repos ='http://cran.us.r-project.org')
```
# Data Exploration

The following document contains some exploration of the datasets. Firstly, some of the most important variables are described with their corresponding data class. Secondly, some plots are made to explore the effect of different variables on the cities in the datasets.

```{r include=FALSE}
library(tidyverse)
```

       

```{r include=FALSE}
# load in the data
airbnb_dataset <- read_csv("../../gen/data-preparation/temp/airbnb_dataset_without_outliers.csv")
```



```{r include=FALSE}
#head statements for all listings
head(airbnb_dataset)
```

## Variable Description

```{r table2, echo=FALSE, message=FALSE, results='asis', warnings=FALSE}
tabl <- "
| Variable      | Description                     | Data class | 
|---------------|:-------------------------------:|-----------:|
| price         | Listing price of room per night | numeric    |
| city          | City of observation             | character  |
| date          | Date of booking                 | Date       |
| room type     | Type of room                    | character  |                                   
| neighbourhood | Neighbourhood of city           | character  |
"
cat(tabl) # table format
```
## Plots

Below you can find the plot for the average price of a listing for an Airbnb from the 25th of April till the fifth of June, for the four cities in the dataset.
```{r echo=FALSE}
# make summary plot of all prices of all cities throughout the year 2022
airbnb_dataset %>%
  ggplot(aes(x = date,
             y = price,
             color = city)) + stat_summary(fun = "mean", geom = "line") + xlab("Date of listing") + ylab("Average price of listing") + theme_classic()

```

Below you can find tables with the different room types and their average price, for the four cities in the dataset.
```{r echo=FALSE}
# make summary plot of price per room type
airbnb_dataset %>%
  ggplot(aes(x = room_type ,
             y = price, fill = room_type)) + stat_summary(fun = "mean", geom = "bar") + facet_wrap(~ city) + xlab("Type of room per city") + ylab("Average price of listing") + theme_classic() 